Synthesising Recursive Functions for\\ First-Order Model Counting

### 2023-03-17 doc/talks/3_long/talk.tex
Improve the slide on the algebraic interpretation of an FCG

\author{Paulius Dilkas \\ \vspace{1cm} \tiny{Joint work with Vaishak Belle (Univeristy of Edinburgh, UK)}}
\title{Synthesising Recursive Functions for\\ First-Order Model Counting}
\institute{National University of Singapore, Singapore}
\date{\today}
% TODO: update the date
% TODO: unify the use of colours
% TODO: do I want to mention forclift and/or crane?
% TODO: maybe replace red!50 with one of the main colours
% TODO: \color -> \textcolor everywhere
% TODO: how do we capitalise blocks?

@@

% TODO: add arrows that explain the meaning/definition of each node type
\begin{frame}{How to Interpret an FCG}
  \begin{columns}
    \begin{column}{0.25\textwidth}
      \centering
      \begin{tikzpicture}[every node/.style={draw,ellipse},edge from parent/.style={draw,-latex},sibling distance=12mm,level distance=15mm]
        \node[fill=red!50,fill on=<2>] (dr) {\textsc{GDR}}
        child {node[fill=red!50,fill on=<3>] {$\bigvee$}
                child {node[fill=red!50, fill on=<4>] {\textsc{CR}}
                  child {node[fill=red!50, fill on=<5>] {$\land$}
                    child {node[fill=red!50, fill on=<6>] {$\bot$}}
                    child {node[fill=red!50, fill on=<7>] (ref) {\textsc{Ref}}}
        }}};
        \draw[-latex, bend right] (ref) to (dr);
      \end{tikzpicture}
    \end{column}
    \begin{column}{0.75\textwidth}
      \begin{align*}
        f(m, n) &= \onslide<3->{\sum_{l=0}^m \binom{m}{l}} \onslide<6->{[l<2]} \onslide<5->{\times} \onslide<7->{f(m-l, n-1)}\\
        \onslide<8>{&= f(m, n-1) + mf(m-1, n-1)}
      \end{align*}
      \onslide<6>{
        \[
          [\phi] =
          \begin{cases}
            1 & \text{if } \phi \\
            0 & \text{if } \neg\phi
          \end{cases}
          \]
      }
    \end{column}
  \end{columns}
\end{frame}

>>>>

\author{Paulius Dilkas \\ \vspace{1cm} \tiny{Joint work with Vaishak Belle (Univeristy of Edinburgh, UK)}}
\title{Synthesising Recursive Functions for\\ First-Order Model Counting}
\institute{National University of Singapore, Singapore}
\date{\today}
% TODO: update the date
% TODO: unify the use of colours
% TODO: do I want to mention forclift and/or crane?
% TODO: maybe replace red!50 with one of the main colours
% TODO: \color -> \textcolor everywhere
% TODO: how do we capitalise blocks?
% TODO: make sure I'm using the 'forest' package whenever possible
% TODO: use Latex and not latex everywhere

@@

\begin{frame}{How to Interpret an FCG}
  \begin{columns}
    \begin{column}{0.25\textwidth}
      \centering
      \vspace{1cm}
      \begin{forest}
        for tree={sn edges}
        [$\GDR$,ellipse,draw,name=gdr,fill=red!50,fill on=<4>
        [$\bigvee$,ellipse,draw,name=bigvee,fill=red!50,fill on=<5>
        [$\CR$,ellipse,draw,name=cr,fill=red!50,fill on=<6>
        [$\land$,ellipse,draw,name=conj,fill=red!50,fill on=<7>
        [$\bot$,rectangle,draw,alt=<8>{fill=red!50}{fill=gray!25},name=contradiction]
        [$\Reff$,ellipse,draw,name=ref,fill=red!50,fill on=<9>]
        ]
        ]
        ]
        ]
        \draw[-Latex,bend right=45] (ref) to (gdr);
        \draw[visible on=<2-3>] (5, 42 |- gdr) node[text width=5cm,name=gdrtwo,text=color2] {\alert<3>{Generalised domain recursion}};
        \draw[visible on=<2-3>] (5, 42 |- bigvee) node[text width=5cm,name=bigveetwo,text=color2] {Deterministic set-disjunction};
        \draw[visible on=<2-3>] (5, 42 |- cr) node[text width=5cm,name=crtwo,text=color2] {\alert<3>{Constraint removal}};
        \draw[visible on=<2-3>] (5, 42 |- conj) node[text width=5cm,name=conjtwo,text=color2] {Decomposable conjunction};
        \draw[visible on=<2-3>] (5, 42 |- ref) node[text width=5cm,name=reftwo,text=color2] {\alert<3>{Caching}};
        \node[visible on=<2-3>,below=0.5cm of contradiction,name=contradictiontwo,text=color2] {Contradiction};
        \draw[visible on=<2-3>,-Latex,dashed,color=color2] (gdrtwo) -- (gdr);
        \draw[visible on=<2-3>,-Latex,dashed,color=color2] (bigveetwo) -- (bigvee);
        \draw[visible on=<2-3>,-Latex,dashed,color=color2] (crtwo) -- (cr);
        \draw[visible on=<2-3>,-Latex,dashed,color=color2] (conjtwo) -- (conj);
        \draw[visible on=<2-3>,-Latex,dashed,color=color2] (reftwo) -- (ref);
        \draw[visible on=<2-3>,-Latex,dashed,color=color2] (contradictiontwo) -- (contradiction);
      \end{forest}
    \end{column}
    \begin{column}{0.75\textwidth}
      \begin{align*}
        \onslide<4->{f(m, n) &=} \onslide<5->{\sum_{l=0}^m \binom{m}{l}} \onslide<8->{[l<2]} \onslide<7->{\times} \onslide<9->{f(m-l, n-1)}\\
        \onslide<10>{&= f(m, n-1) + mf(m-1, n-1)}
      \end{align*}
      \onslide<8>{
        \[
          [\phi] =
          \begin{cases}
            1 & \text{if } \phi \\
            0 & \text{if } \neg\phi
          \end{cases}
          \]
      }
    \end{column}
  \end{columns}
\end{frame}
